---
title: "Can the wisdom of crowds guess celebrity ages?"
subtitle: "STA 199"
date: 01/09/2025
author: Insert Your Name
format: pdf
---

# Setup

## Load packages

```{r}
#| message: false

```

## Load in the data

```{r}
#| message: false

```

{{< pagebreak >}}

# Celebrity 1

## Compute numerical summaries

```{r}

```

## Plot the data

```{r}
#| message: false


```

-   **Born**: 2/10/1987
-   **Age in photo**:
-   **Claim to fame**:

{{< pagebreak >}}

# Celebrity 2

## Compute numerical summaries

```{r}
#| eval: false
typical_guess2 <- age_guesses |>
  summarize(mean_guess = mean(celeb2), 
            median_guess = median(celeb2))
typical_guess2
```

## Plot the data

```{r}
#| message: false
#| eval: false

ggplot(age_guesses, aes(x = celeb2)) + 
  geom_histogram() + 
  geom_rect(aes(xmin = 38, xmax = 42, ymin = 0, ymax = Inf), fill = "darkgreen") + 
  labs(x = "Age", title = "Age guesses for XYZ") + 
  geom_vline(data = typical_guess2, aes(xintercept = mean_guess), color = "red") + 
  geom_vline(data = typical_guess2, aes(xintercept = median_guess), color = "blue")
```

-   **Born**:
-   **Died**: 5/10/1977
-   **Age in photo**:
-   **Claim to fame**:

{{< pagebreak >}}

# Celebrity 3

## Compute numerical summaries

```{r}
#| eval: false

typical_guess3 <- age_guesses |>
  summarize(mean_guess = mean(celeb3), 
            median_guess = median(celeb3))
typical_guess3
```

## Plot the data

```{r}
#| message: false
#| eval: false

ggplot(age_guesses, aes(x = celeb3)) + 
  geom_histogram() + 
  labs(x = "Age", title = "Age guesses for XYZ") + 
  geom_vline(data = typical_guess3, aes(xintercept = mean_guess), color = "red") + 
  geom_vline(data = typical_guess3, aes(xintercept = median_guess), color = "blue") +
  geom_vline(xintercept = 0, color = "darkgreen")
```

-   **Born**: 2/7/1887 
-   **Died**: 2/12/1983
-   **Age in photo**:
-   **Claim to fame**:

{{< pagebreak >}}

# Celebrity 4

## Compute numerical summaries

```{r}
#| eval: false

typical_guess4 <- age_guesses |>
  summarize(mean_guess = mean(celeb4), 
            median_guess = median(celeb4))
typical_guess4
```

## Plot the data

```{r}
#| message: false
#| eval: false

ggplot(age_guesses, aes(x = celeb4)) + 
  geom_histogram() + 
  labs(x = "Age", title = "Age guesses for XYZ") + 
  geom_vline(data = typical_guess4, aes(xintercept = mean_guess), color = "red") + 
  geom_vline(data = typical_guess4, aes(xintercept = median_guess), color = "blue") +
  geom_vline(xintercept = 0, color = "darkgreen")
```

-   **Born**: 2/3/1963
-   **Age in photo**:
-   **Claim to fame**:

{{< pagebreak >}}

# Celebrity 5

## Compute numerical summaries

```{r}
#| eval: false

typical_guess5 <- age_guesses |>
  summarize(mean_guess = mean(celeb5), 
            median_guess = median(celeb5))
typical_guess5
```

## Plot the data

```{r}
#| message: false
#| eval: false

ggplot(age_guesses, aes(x = celeb5)) + 
  geom_histogram() + 
  labs(x = "Age", title = "Age guesses for XYZ") + 
  geom_vline(data = typical_guess5, aes(xintercept = mean_guess), color = "red") + 
  geom_vline(data = typical_guess5, aes(xintercept = median_guess), color = "blue") +
  geom_vline(xintercept = 0, color = "darkgreen")
```

-   **Born**: 9/18/1961
-   **Died**: 6/19/2013
-   **Age in photo**:
-   **Claim to fame**:

{{< pagebreak >}}

# Celebrity 6

## Compute numerical summaries

```{r}
#| eval: false

typical_guess6 <- age_guesses |>
  summarize(mean_guess = mean(celeb6), 
            median_guess = median(celeb6))
typical_guess6
```

## Plot the data

```{r}
#| message: false
#| eval: false

ggplot(age_guesses, aes(x = celeb6)) + 
  geom_histogram() + 
  labs(x = "Age", title = "Age guesses for XYZ") + 
  geom_vline(data = typical_guess6, aes(xintercept = mean_guess), color = "red") + 
  geom_vline(data = typical_guess6, aes(xintercept = median_guess), color = "blue") +
  geom_vline(xintercept = 0, color = "darkgreen")
```

-   **Born**: 10/21/1925
-   **Died**: 7/16/2003
-   **Age in photo**:
-   **Claim to fame**:
